%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://piymis.com/}{\Large Piyush Mishra}} & Email : \href{mailto:piymis6@gmail.com}{piymis6@gmail.com}\\
  \href{https://piymis.com/}{https://piymis.com/} & Mobile : +91-9911669538 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Delhi Technological University}{Delhi, India}
      {Bachelor of Technology in Electronics and Communication;  GPA: 8.1/10.0}{Aug. 2011 -- May. 2015}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Goibibo}{Bangalore, India}
      {Sr. Software Engineer 2}{October 2019 - Present}
      \resumeItemListStart
        \resumeItem{InGoMMT Extranet Portal}
          {Developing and maintaining backend services for Goibibo and MakeMyTrip hotelier platform.}
        \resumeItem{InGoMMT Extranet Portal}
          {Worked on User Generated Content, Google drive integration and creation of REST APIs.}
        \resumeItem{InGoMMT Extranet Portal}
          {Developed the full video backend functionality, with compression techniques to save bandwidth and optimize cost.}

      \resumeItemListEnd

    \resumeSubheading
      {Amadeus}{Bangalore, India}
      {Sr. Software Engineer}{July 2015 - October 2019}
      \resumeItemListStart
        \resumeItem{Channel Hub}
          {Developing REST APIs to handle shopping and booking transactions for Hotel IT platform.}
        \resumeItem{Rail OBE}
          {Developed Open Backend (OBE) components for rail web services distribution platform.}
        \resumeItem{SPEAR}
          {Developed web application and REST API for managing of passenger record data.}
        \resumeItem{ALF Library}
          {Developed python library for internal issue tracking system.}
        \resumeItem{Data Integrity Checker}
          {Tool to check data integrity among databases having incompatible schema.}
        \resumeItem{Load Coordinator}
          {Global production load coordinator for rail business unit.}
        \resumeItem{Mentorship}
          {Mentoring and grooming of interns.}      
      \resumeItemListEnd
      
   \resumeSubHeadingListEnd

% --------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
    \item{
     \textbf{Languages}{: C, C++, Python, Javascript, Java, Shell scripting}
    }
    \item{
     \textbf{Frameworks}{: Django, Flask, React, Bootstrap}
    }
    \item{
     \textbf{Technologies}{: Redis, Celery, Kafka, MySQL, MongoDB, Docker, AWS, Protobuf, Jenkins}
    }
 \resumeSubHeadingListEnd
 
% --------Workshops ------------ 
\section{Workshops}
 \resumeSubHeadingListStart
    \resumeSubItem{Texas Instruments}
      {Linux Kernel Driver Development on Beaglebone Black.}
    \resumeSubItem{Agile Asia}
      {Behavior driven development using Java and Python.}
 \resumeSubHeadingListEnd 
 
% --------Awards ------------ 
\section{Recognitions}
 \resumeSubHeadingListStart
     \item{
     {Winner at Futurize hackathon for AI-based hotel concierge chatbot using Amazon Lex integrated with Alexa.}
    }
     \item{
     {Recognized and awarded best performer four times at work.}
    }
     \item{
      {Scored top 0.2\% among 1.2 million aspirants in IIT JEE and AIEEE 2011 examinations.}
    }
 \resumeSubHeadingListEnd  
 
% --------Courses ------------ 
\section{Online Courses}
 \resumeSubHeadingListStart
    \item{
     \textbf{Introduction to Computer Science and
     Programming}{: Massachusetts Institute of Technology}
    }
    \item{
     \textbf{Algorithmic Toolbox and Data Structures}{: University of California San Diego}
    }
    \item{
     \textbf{Heterogeneous Parallel Programming}{: University of Illinois at Urbana-Champaign}
    }
    
 \resumeSubHeadingListEnd 
 
%-------------------------------------------
\end{document}
